Bayesian Modeling and Test Planning for Multi-phase Reliability Assessment

### 2018-01-27 paperDraft3.tex
finished edits

Figure~\ref{fig:CAP} shows the posterior distributions for each of the FEF parameters $\rho_{j}^{P2}$ and $\rho_{j}^{P3}$ for the hierarchical Weibull model.  These parameters were introduced in Section~\ref{FEF}.  They are multiplicative parameters added in between phases to capture the change in failure rate due to improvements by the producer.  Values less than one indicate a decrease in failure rate.  The distributions look reasonable with most of the mass close to one.  We notice a trend of more improvement in the second CAP between phase two and three compared to the first CAP between phase one and two.

@@

We consider fully Bayesian posterior risks, which provides a
different interpretation from the corresponding classical risks.  While the classical approach
provides assurance that satisfactory devices will pass the test and that
unsatisfactory devices will fail it, posterior risks provide precisely the
assurance that practitioners often desire: if the test is passed, then the
consumer desires a maximum probability $\beta_b$ that \textcolor{blue}{the true reliability is less than the rejectable level,} $\pi \leq \pi_1$. On the
other hand, if the test is failed, then the producer desires a maximum
probability $\alpha_b$ \textcolor{blue}{the true reliability is greater than the acceptable level,} that $\pi \geq \pi_0$. Notice these posterior risks are fully Bayesian in the sense that they are probability statements about $\pi$.

@@

\textcolor{blue}{Table 2 compares the resulting test plans of our proposed method to the classical method.  In the classical case we only controlled for the consumer's risk, because with the proposed values of  $\pi_0$, $\pi_1$, $\alpha_c$ and allowed failures there was no test mileage that would satisfy both risk criteria.  In general, we warn against making this comparison of test plans, because each method makes different assumptions and the test plan probability constraints are asking different questions.  The classical plan assumes product is either acceptable or unacceptable and then controls the probability of error in each of those cases.  On the other hand, the Bayesian plan puts constraints on the probability of error when the test is passed and failed.}

@@

In this paper we have focused on test plans for single units, but the assurance testing methodology can be extended to find test plans that
allow for a changing number of testing units.  In this case you would find
9combinations of failures allowed and test miles required and number of vehicles
tested that satisfy the risk requirements. More details and examples of this can
be found in Hamada et al. ~\cite{ref4}

@@

%%%%% ref %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{99}
\bibitem{ref1} Director, Defense Test and Evaluation. Test and evaluation of system reliability availability maintainability - A primer; Third Edition (1982).
\bibitem{ref2} P.\ M.\ Ellner and J.\ B.\ Hall, An approach to reliability
growth planning based on failure mode discovery and correction using AMSAA
projection methodology. \textit{IEEE Proceedings of the Annual Reliability and
Maintainability Symposium} (2006).
\bibitem{ref3} National Research Council. Statistics, Testing, and Defense
Acquisition: Background Papers. \textit{National Academies Press} (1999).
\bibitem{ref4} M.\ S.\ Hamada, A.\ G.\ Wilson, C.\ S.\ Reese and H.\ F.\ Martz.
Bayesian Reliability. Springer (2008).
\bibitem{ref5} D.\ J.\ Spiegelhalter, N.\ Best, B.\ Carlin, and A.\ Van der
Linde Bayesian measures of model complexity and fit. \textit{Royal Statistical
Society}, Series B, 64: 583–640 (2002).
\bibitem{ref6} Gelman, Andrew, Xiao-Li Meng, and Hal Stern. Posterior
predictive assessment of model fitness via realized discrepancies. (1996)
\bibitem{ref7} W.\ Q.\ Meeker and L.\ A.\ Escobar. Reliability: the other
dimension of quailty. \textit{Quality Technology and Quantitative Management} 1,
1-25 (2004).
\bibitem{ref8} \textcolor{red}{Need to find}
\bibitem{ref9} B. Weaver, M. Hamada, A. Wilson, J. Bakerman (2017). Bayesian Assurance Tests for Degradation Data. Quality and Reliability Engineering International 33(8): 2699-2709.
\end{thebibliography}

@@

Full conditionals for Gibbs sampling:
\begin{align*}
\lambda_i|\cdot &\sim \text{Gamma}(n_i + \alpha, \sum_{j=1}^{n_i}y_{ij}p^* + \beta) \\
\beta|\cdot &\sim \text{Gamma}(8\alpha + b_1, \sum{\lambda_i} + b_2) \\
\rho^{P2}|\cdot &\sim \text{Gamma}(N_{1,2} + c_1, \sum{y_{ij}\lambda_i} + c_2) \\
\rho^{P3}|\cdot &\sim \text{Gamma}(N_{2} + d_1, \sum{y_{ij}\lambda_i} + d_2) \\
\alpha|\cdot &\sim \text{Unknown form.  Used Metropolis-Hastings.}
\end{align*}

@@

Full conditionals for Gibbs sampling:
\begin{align*}
\lambda_i|\cdot &\sim \text{Gamma}(n_i + \alpha, \sum_{j=1}^{n_i}t_{ij}^{\gamma_i} p^* + \beta) \\
\beta|\cdot &\sim \text{Gamma}(8\alpha + b_1, \sum{\lambda_i} + b_2) \\
\rho^{P2}|\cdot &\sim \text{Gamma}(N_{1,2} + c_1, \sum{t_{ij}^{\gamma_i} \lambda_i} + c_2) \\
\rho^{P3}|\cdot &\sim \text{Gamma}(N_{2} + d_1, \sum{t_{ij}^{\gamma_i} \lambda_i} + d_2) \\
\alpha|\cdot &\sim \text{Unknown form.  Used Metropolis-Hastings.}\\
\gamma|\cdot &\sim \text{Unknown form.  Used Metropolis-Hastings.}
\end{align*}

>>>>

Figure~\ref{fig:CAP} shows the posterior distributions for each of the CAP parameters $\rho_{j}^{P2}$ and $\rho_{j}^{P3}$ for the hierarchical Weibull model.  These parameters were introduced in Section~\ref{FEF}.  They are multiplicative parameters added in between phases to capture the change in failure rate due to improvements by the producer.  Values less than one indicate a decrease in failure rate.  The distributions look reasonable with most of the mass close to the commonly used FEF value of 0.70.  We notice a trend of more improvement in the second CAP between phase two and three compared to the first CAP between phase one and two.

@@

We consider fully Bayesian posterior risks, which provides a
different interpretation from the corresponding classical risks.  While the classical approach
provides assurance that satisfactory devices will pass the test and that
unsatisfactory devices will fail it, posterior risks provide precisely the
assurance that practitioners often desire: if the test is passed, then the
consumer desires a maximum probability $\beta_b$ that the true reliability is less than the rejectable level, $\pi \leq \pi_1$. On the
other hand, if the test is failed, then the producer desires a maximum
probability $\alpha_b$ the true reliability is greater than the acceptable level, that $\pi \geq \pi_0$. Notice these posterior risks are fully Bayesian in the sense that they are probability statements about $\pi$.

@@

Table 2 compares the resulting test plans of our proposed method to the classical method.  In the classical case we only controlled for the consumer's risk, because with the proposed values of  $\pi_0$, $\pi_1$, $\alpha_c$ and allowed failures there was no test mileage that would satisfy both risk criteria.  Notice this leads to extremely high levels of producer risk under the classical plan.  In general, we warn against making this comparison of test plans, because each method makes different assumptions and the test plan probability constraints are asking different questions.  The classical plan assumes product is either acceptable or unacceptable and then controls the probability of error in each of those cases.  On the other hand, the Bayesian plan puts constraints on the probability of error when the test is passed and failed.

@@

In this paper we have focused on test plans for single units, but the assurance testing methodology can be extended to find test plans that
allow for a changing number of testing units.  In this case you would find
combinations of failures allowed and test miles required and number of vehicles
tested that satisfy the risk requirements. More details and examples of this can
be found in Hamada et al. ~\cite{ref4}

@@

%%%%% ref %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{99}
\bibitem{ref1} Director, Defense Test and Evaluation. Test and evaluation of system reliability availability maintainability - A primer; Third Edition 1982.
\bibitem{ref2} P.\ M.\ Ellner, J.\ B.\ Hall. An approach to reliability
growth planning based on failure mode discovery and correction using AMSAA
projection methodology. \textit{IEEE Proceedings of the Annual Reliability and
Maintainability Symposium} 2006.
\bibitem{ref3} National Research Council. Statistics, Testing, and Defense
Acquisition: Background Papers. \textit{National Academies Press} 1999.
\bibitem{ref4} M.\ Hamada, A.\  Wilson, C.\ Reese, H.\ Martz. Bayesian Reliability. Springer 2008.
\bibitem{ref5} D.\  Spiegelhalter, N.\ Best, B.\ Carlin, A.\ Van der
Linde Bayesian measures of model complexity and fit. \textit{Royal Statistical
Society}, Series B, 64: 583-640 2002.
\bibitem{ref6} A. Gelman, M. Xiao-Li, H. Stern. Posterior predictive assessment of model fitness via realized discrepancies (with discussion). \textit{Statist. Sin.} 6, 733-807 1996.
\bibitem{ref7} W.\ Meeker, L.\ Escobar. Reliability: the other
dimension of quailty. \textit{Quality Technology and Quantitative Management} 1, 1-25 2004.
\bibitem{ref8} J.\ F.\ Lawless. Statistical Models and Methods for Lifetime Data, 2nd Edition. John Wiley \& Sons 2011.
\bibitem{ref9} B.\ Weaver, M.\ Hamada, A.\ Wilson, J.\ Bakerman. Bayesian Assurance Tests for Degradation Data. \textit{Quality and Reliability Engineering International} 33(8): 2699-2709  2017.
\end{thebibliography}

@@

Full conditionals for Gibbs sampling:
\begin{align*}
\lambda_i|\cdot &\sim \text{Gamma}(n_i + \alpha, \sum_{j=1}^{n_i}y_{ij}p^* + \beta) \\
\beta|\cdot &\sim \text{Gamma}(8\alpha + b_1, \sum{\lambda_i} + b_2) \\
\rho^{P2}|\cdot &\sim \text{Gamma}(N_{1,2} + c_1, \sum{y_{ij}\lambda_i} + c_2) \\
\rho^{P3}|\cdot &\sim \text{Gamma}(N_{2} + d_1, \sum{y_{ij}\lambda_i} + d_2) \\
\alpha|\cdot &\sim \prod_{i = 1}^8 \Bigg[\prod_{j =1}^R \frac{\beta^\alpha}{\Gamma(\alpha)}\lambda_i^{\alpha -
  1}\Bigg] (\alpha^{a_1-1}e^{-\alpha a_2}) \text{(Metropolis-Hastings used for sampling)}
\end{align*}

@@

Full conditionals for Gibbs sampling:
\begin{align*}
\lambda_i|\cdot &\sim \text{Gamma}(n_i + \alpha, \sum_{j=1}^{n_i}t_{ij}^{\gamma_i} p^* + \beta) \\
\beta|\cdot &\sim \text{Gamma}(8\alpha + b_1, \sum{\lambda_i} + b_2) \\
\rho^{P2}|\cdot &\sim \text{Gamma}(N_{1,2} + c_1, \sum{t_{ij}^{\gamma_i} \lambda_i} + c_2) \\
\rho^{P3}|\cdot &\sim \text{Gamma}(N_{2} + d_1, \sum{t_{ij}^{\gamma_i} \lambda_i} + d_2) \\
\alpha|\cdot &\sim \prod_{i = 1}^8 \Bigg[\prod_{j =1}^R \frac{\beta^\alpha}{\Gamma(\alpha)}\lambda_i^{\alpha -
  1}\Bigg] (\alpha^{a_1-1}e^{-\alpha a_2}) \text{(Metropolis-Hastings used for sampling)}\\
\gamma|\cdot &\sim \prod_{i = 1}^8 \Bigg[ \prod_{j = 1}^{n_j}(t_{ij}^{\gamma_i-1} e^{-t_{ij}^{\gamma_i}})\prod_{j = 1}^R(e^{-t_{ij}^{\gamma_i}}) \Bigg] (\gamma^{g_1 - 1}e^{-\gamma g_2}) \text{(Metropolis-Hastings used for sampling)}
\end{align*}
